---
title: "Notes on Codes"
output: github_document
---

output:
  html_document:
    toc: true
    toc_float: true

# Loarding packages
  * load all pacakges in the begining so anybody opening the document would have a clear idea on which packages are used.
```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

# Data Import
  * `read_csv`
  * `read_excel`
  * `read_sas`

# Data Export
 * `write_csv`

# Look at Data and Clean Name
* `janitor::clean_names(litters_df)`
* `head(litters_df)`
* `tail(litters_df)`
* `skimr::skim(litters_df)`

## Data Import Example

### read_csv
```{r, eval = FALSE}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df) 
```

```{r, eval = FALSE}
litters_df = read_csv("./data/Fas_litters.csv", skip = 10, col_names = FALSE)
```

```{r, eval = FALSE}
litters_df = read_csv("./data/Fas_litters.csv", na = c("","NA", 999))
```

### read_excel
```{r, eval = FALSE}
mlb_df = read_excel("./data/mlb11.xlsx")
mlb_df
```

```{r, eval = FALSE}
mlb_df = read_excel("./data/mlb11.xlsx", range = "A1:F7")
mlb_df
```

### read_sas.
```{r, eval = FALSE}
pulse_df = read_sas("./data/public_pulse_data.sas7bdat")
pulse_df
```

## Data Export Example
### Export the mlb sub-table.
```{r, eval = FALSE}
mlb_df
```

```{r, eval = FALSE}
write_csv(mlb_df, "./data/mlb_subtable.csv")
```




